---
title: "Storm Analysis"
output: html_document
---

## Data Processing  

Download the file of the [storm data](http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2); and then unzip it and read the data into a data frame 

```{r cache=TRUE}
## create a temporary file
temp <- tempfile();
## download the compressed bz2 file from web site
download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", temp, mode="wb")
## decompress and read the file data to a data frame called "data"
data <- read.csv(bzfile(temp))
## delete the temporary file
unlink(temp)
```

Recategorize the event types

```{r cache=TRUE}
evtypes <- c("ASTRONOMICAL LOW TIDE","AVALANCHE","BLIZZARD","COASTAL FLOOD","COLD/WIND CHILL","DEBRIS FLOW","DENSE FOG","DENSE SMOKE","DROUGHT","DUST DEVIL","DUST STORM","EXCESSIVE HEAT","EXTREME COLD/WIND CHILL","FLASH FLOOD","FLOOD","FROST/FREEZE","FUNNEL CLOUD","FREEZING FOG","HAIL","HEAT","HEAVY RAIN","HEAVY SNOW","HIGH SURF","HIGH WIND","HURRICANE(TYPHOON)","ICE STORM","LAKE EFFECT SNOW","LAKESHORE FLOOD","LIGHTNING","MARINE HAIL","MARINE HIGH WIND","MARINE STRONG WIND","MARINE THUNDERSTORM WIND","RIP CURRENT","SEICHE","SLEET","STORM SURGE/TIDE","STRONG WIND","THUNDERSTORM WIND","TORNADO","TROPICAL DEPRESSION","TROPICAL STORM","TSUNAMI","VOLCANIC ASH","WATERSPOUT","WILDFIRE","WINTER STORM","WINTER WEATHER")
names(evtypes) <- evtypes

data$EVTYPENEW <- data$EVTYPE

## AVALANCHE
levels(data$EVTYPENEW)[grepl("AVALANC",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[2]
## BLIZZARD
levels(data$EVTYPENEW)[grepl("BLIZZARD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[3] 
## Coastal flood
levels(data$EVTYPENEW)[grepl("COASTAL.*FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[4]
levels(data$EVTYPENEW)[grepl("COASTAL.*SURGE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[4]
levels(data$EVTYPENEW)[grepl("BEACH FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[4]
levels(data$EVTYPENEW)[grepl("CSTL FLOODING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <- evtypes[4]
## COLD/WIND CHILL
levels(data$EVTYPENEW)[grepl("COLD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[5]
levels(data$EVTYPENEW)[grepl("WIND CHILL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[5]
levels(data$EVTYPENEW)[grepl("LOW TEMPERATURE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[5]
## Dense fog
levels(data$EVTYPENEW)[grepl("PATCHY DENSE FOG",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[7]
## Drought
levels(data$EVTYPENEW)[grepl("DROUGHT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[9]
levels(data$EVTYPENEW)[grepl("DRY",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[9]
levels(data$EVTYPENEW)[grepl("BELOW NORMAL PRECIPITATION",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[9]
## Dust devel
levels(data$EVTYPENEW)[grepl("DUST.*DEV",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[10]
## Dust storm
levels(data$EVTYPENEW)[grepl("DUST.*STORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[11]
levels(data$EVTYPENEW)[grepl("SAHARAN DUST",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[11]
levels(data$EVTYPENEW)[grepl("BLOWING DUST",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[11]
## Excessive heat
levels(data$EVTYPENEW)[grepl("EXCESSIVE.*HEAT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[12]
levels(data$EVTYPENEW)[grepl("HIGH TEMPERATURE RECORD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[12]
levels(data$EVTYPENEW)[grepl("RECORD HEAT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[12]
levels(data$EVTYPENEW)[grepl("RECORD HIGH",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[12]
## Extreme code or wind chill
levels(data$EVTYPENEW)[grepl("EXTREME.*WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[13]
levels(data$EVTYPENEW)[grepl("RECORD LOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[13]
## Flash flood
levels(data$EVTYPENEW)[grepl("FLASH.*FLOO",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[14]
levels(data$EVTYPENEW)[grepl("BREAKUP FLOODING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[14]
## Flood
levels(data$EVTYPENEW)[grepl("^FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("RIVER FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("RURAL FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("URBAN.*FL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("STREAM FL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("STREET FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("TIDAL FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("HIGHWAY FLOODING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("LOCAL FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("MAJOR FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
levels(data$EVTYPENEW)[grepl("MINOR FLOODING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[15]
## Frost or freeze
levels(data$EVTYPENEW)[grepl("FROST",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[16]
levels(data$EVTYPENEW)[grepl("^FREEZE$",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[16]
levels(data$EVTYPENEW)[grepl("HARD FREEZE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[16]
## Funnel cloud
levels(data$EVTYPENEW)[grepl("FUNNEL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[17]
## Freezing fog
levels(data$EVTYPENEW)[grepl("^FREEZING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[18]
## Hail
levels(data$EVTYPENEW)[grepl("^HAIL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[19]
levels(data$EVTYPENEW)[grepl("DEEP HAIL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[19]
levels(data$EVTYPENEW)[grepl("NON SEVERE HAIL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[19]
levels(data$EVTYPENEW)[grepl("SMALL HAIL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[19]
## Heat
levels(data$EVTYPENEW)[grepl("^HEAT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[20]
levels(data$EVTYPENEW)[grepl("HOT SPELL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[20]
levels(data$EVTYPENEW)[grepl("HOT WEATHER",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[20]
## Heavy rain
levels(data$EVTYPENEW)[grepl("HEAVY RAIN",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("HVY RAIN",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("HEAVY PRECIP",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("HEAVY SHOWER",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("EXCESSIVE PRECIPITATIO",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("EXCESSIVE.*RAIN.*",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("PROLONGED RAIN",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("RAIN (HEAVY)",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("RAINSTORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("RECORD RAINFALL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("RECORD PRECIPITATION",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
levels(data$EVTYPENEW)[grepl("TORRENTIAL RAIN",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[21]
## Heavy snow
levels(data$EVTYPENEW)[grepl("HEAVY SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
levels(data$EVTYPENEW)[grepl("HEAVY WET SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
levels(data$EVTYPENEW)[grepl("RECORD SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
levels(data$EVTYPENEW)[grepl("SNOW SQUALL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
levels(data$EVTYPENEW)[grepl("SNOWFALL RECORD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
levels(data$EVTYPENEW)[grepl("BLOWING SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[22]
## High surf
levels(data$EVTYPENEW)[grepl("HEAVY SURF",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
levels(data$EVTYPENEW)[grepl("HEAVY SEAS",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
levels(data$EVTYPENEW)[grepl("HIGH SURF",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
levels(data$EVTYPENEW)[grepl("HIGH SEAS",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
levels(data$EVTYPENEW)[grepl("HIGH WAVES",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
levels(data$EVTYPENEW)[grepl("HAZARDOUS SURF",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[23]
## High wind
levels(data$EVTYPENEW)[grepl("^HIGH.*WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[24]
## Hurricane (typhoon)
levels(data$EVTYPENEW)[grepl("HURRICANE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[25]
levels(data$EVTYPENEW)[grepl("TYPHOON",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[25]
levels(data$EVTYPENEW)[grepl("COASTAL.*STORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[25]
## Ice storm
levels(data$EVTYPENEW)[grepl("^ICE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[26]
levels(data$EVTYPENEW)[grepl("GLAZE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[26]
## Lake effect snow
levels(data$EVTYPENEW)[grepl("LAKE.*EFFECT SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[27]
levels(data$EVTYPENEW)[grepl("HEAVY LAKE SNOW",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[27]
## lake shore flood
levels(data$EVTYPENEW)[grepl("LAKE.*FLOOD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[28]
## Lightning
levels(data$EVTYPENEW)[grepl("LIG.*ING",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[29]
## Marine hail
levels(data$EVTYPENEW)[grepl("MARINE HAIL",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[30]
## Marine high wind
levels(data$EVTYPENEW)[grepl("MARINE HIGH WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[31]
## Marine strong wind
levels(data$EVTYPENEW)[grepl("MARINE STRONG WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[32]
## Marine thunderstorm wind
levels(data$EVTYPENEW)[grepl("MARINE THUNDERSTORM WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[33]
levels(data$EVTYPENEW)[grepl("MARINE TSTM WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[33]
## Rip current
levels(data$EVTYPENEW)[grepl("RIP CURRENT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[34]
## Seiche
levels(data$EVTYPENEW)[grepl("SEICHE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[35]
## Sleet
levels(data$EVTYPENEW)[grepl("SLEET",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[36]
## Storm surge or tide
levels(data$EVTYPENEW)[grepl("STORM SURGE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("BLOW-OUT TIDE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("RAPIDLY RISING WATER",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("HEAVY SWELLS",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("HIGH.*SWELLS",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("HIGH TIDES",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
levels(data$EVTYPENEW)[grepl("HIGH WATER",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[37]
## Strong wind
levels(data$EVTYPENEW)[grepl("STRONG WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[38]
levels(data$EVTYPENEW)[grepl("GUSTNADO",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[38]
levels(data$EVTYPENEW)[grepl("DOWNBURST",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[38]
levels(data$EVTYPENEW)[grepl("GUSTY WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[38]
## Thunderstorm wind
levels(data$EVTYPENEW)[grepl("^THU",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[39]
levels(data$EVTYPENEW)[grepl("^TUNDERSTORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[39]
levels(data$EVTYPENEW)[grepl("^TSTM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[39]
levels(data$EVTYPENEW)[grepl("TSTM WIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[39]
levels(data$EVTYPENEW)[grepl("SEVERE THUNDERSTORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[39]
## Tornado
levels(data$EVTYPENEW)[grepl("^TORN",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[40]
levels(data$EVTYPENEW)[grepl("WHIRLWIND",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[40]
## Tropical depression
levels(data$EVTYPENEW)[grepl("TROPICAL DEPRESSION",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[41]
## TROPICAL STORM
levels(data$EVTYPENEW)[grepl("TROPICAL STORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[42]
## TSUNAMI
levels(data$EVTYPENEW)[grepl("TSUNAMI",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[43]
## VOLCANIC ASH
levels(data$EVTYPENEW)[grepl("VOLCANIC",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[44]
## WATERSPOUT
levels(data$EVTYPENEW)[grepl("WA.*SPOUT",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[45]
## Wildfire
levels(data$EVTYPENEW)[grepl("WILD",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[46]
levels(data$EVTYPENEW)[grepl("FOREST FIRES",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[46]
levels(data$EVTYPENEW)[grepl("BRUSH FIRE",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[46]
levels(data$EVTYPENEW)[grepl("GRASS FIRES",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[46]
## Winter storm
levels(data$EVTYPENEW)[grepl("WINTER STORM",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[47]
## Winter weather
levels(data$EVTYPENEW)[grepl("WINTER WEATHER",levels(data$EVTYPENEW), ignore.case=TRUE, perl=TRUE)] <-  evtypes[48]

## create the new "Other" event type to the rest of the events
other <- !(data$EVTYPENEW %in% evtypes)
tmp <- as.character(data$EVTYPENEW)
tmp[other] <- "Other"
data$EVTYPENEW <- factor(tmp)
```

## Data Analysis

### Question 1:  
### Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

**calculate the total fatalities and injuries by the new event types

```{r}
casualties <- aggregate(FATALITIES + INJURIES ~ EVTYPENEW,data=data, sum)
names(casualties) <- c("EVTYPENEW","CASAULTIES")
highestCasualties <- casualties[casualties$CASAULTIES==max(casualties$CASAULTIES),]

#install.packages("ggplot2")
library(ggplot2)
ggplot(casualties, aes(x=EVTYPENEW, y=CASAULTIES)) + geom_bar(stat="identity") + labs(title="Total Casualties in the USA by Storm Type from 1950 to 2011", x="Storm Type", y="Casualty (Fatality + Injury) Count") + theme(axis.text.x = element_text(angle = 90, vjust = 0))
```

**The storm with highest rate of casualties is** *`r highestCasualties$EVTYPENEW`*  

### Question 2: 
### Across the United States, which types of events have the greatest economic consequences?


## Results
```{r}

```

